Fail Faster

### 2025-03-17 paper/paper.tex
transpose

\section{Eliminating Abstraction Overhead of Generator DSLs by Staging and Faster Randomness Libraries}
\jwc{This section needs a much better title...}
\jwc{Emphasize that this is an \emph{COMPLETELY EQUIVALENT drop in replacement!} We din't just build a different library with different distributions.}

@@

\subsection{Design of a Staged Generator DSL}
\label{subsection:basic-design}
Recall that staging a DSL involves changing the
combinators to run at compile time by carefully annotating their types with \texttt{code}s.
Deciding which types \texttt{t} can
instead be \texttt{t code} --- in other words,
figuring out which parts of the DSL can be determined statically (and can be
part of the compile-time stage), and which parts are only known dynamically (and
hence must be \texttt{code}) --- is an art known as ``binding-time analysis'' \cn.

>>>>

\section{Speeding up Generator DSLs by Staging and Faster Randomness Libraries}
\jwc{This section needs a much better title...}
\jwc{Emphasize that this is an \emph{COMPLETELY EQUIVALENT drop in replacement!} We din't just build a different library with different distributions.}

@@

\subsection{Design of a Staged Generator DSL}
\label{subsection:basic-design}
\jwc{Needs a lot more signposting at the top here.}

Recall \jwc{did we talk about this} that staging a DSL involves changing the
combinators to run at compile time by carefully annotating their types with \texttt{code}s.
Deciding which types \texttt{t} can
instead be \texttt{t code} --- in other words,
figuring out which parts of the DSL can be determined statically (and can be
part of the compile-time stage), and which parts are only known dynamically (and
hence must be \texttt{code}) --- is an art known as ``binding-time analysis'' \cn.
